An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-30 realization.tex
Updated verification section

\subsubsection{Practical verification against a Verifier} 
Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}. The Prolog implementation was used in their research to formally verify their proposed approach for the generation of co-simulation algorithms. The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm. As a part of this work, an integration from the developed plugin has been realized to interact with the Prolog Verifier. This integration has been realized to verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Generator and Verifier. The integration works by querying the Prolog database with a co-simulation environment and a calculated initialization to verify the order's correctness. The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations. This transformation is based on the definitions \ref{def:getout} and \ref{def:setin}. The described verification integration is not utilized if the graph contains algebraic loops since the Prolog database does not support these scenarios.

The Prolog code can generate an initialization order, but this functionality has not been used for several reasons. The main reason for not creating the initialization order using the Prolog code is based on performance considerations. The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.

>>>>

\subsubsection{Practical verification against a Verifier} 
Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation formulated in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}. The Prolog implementation was used in their research to verify their approach for generating co-simulation algorithms formally. The Prolog realization encapsulates all the rules of a valid co-simulation step (both master-algorithm and an initialization algorithm). 
This work includes an integration from the developed plugin to the Prolog Verifier. The integration has been realized to systematically verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Verifier. The integration queries the Prolog database with a co-simulation environment and a calculated initialization order to verify the order's correctness. The integration performs all the necessary transformations of the dependency graph (see definition \ref{def:initialization_graph}) used in the Maestro plugin to a graph of FMU operations used in the Prolog database. The transformation is based on the definitions \ref{def:getout} and \ref{def:setin}. The Prolog integration is not applied if the graph contains algebraic loops since the Prolog database does not support these scenarios.

The Prolog code is capable of generating a valid initialization order, but this functionality is not used for several reasons. The main reasons are based on performance considerations and the desire to handle the initialization of co-simulation scenarios containing strongly connected components.
